Multiple Comparisons in Toolmark Evidence

### 2023-11-22 LPR/index.qmd

If we start out by considering the first scenario (a single tool with a 1.5 cm blade compared to a single 2mm wire) and completely independent non-overlapping comparisons (7.5 comparisons) with only 2 cutting surfaces, we would effectively have 15 independent comparisons. Using this information, we can calculate the probability of at least one false positive error to be `r sprintf("%0.04f%%", 1-(1-fpr)^comparisons * 100)` as shown in Equation \ref{eq:fpr}. While far more comparisons are likely to be performed, these comparisons may have some dependencies (at which point our formula would need to account for the covariance between successive comparisons). Ultimately, the number of comparisons cannot drop below `r comparisons` without leaving some evidence unexamined, which means this overall false positive rate is the lower bound.

>>>>

If we start out by considering the first scenario (a single tool with a 1.5 cm blade compared to a single 2mm wire) and completely independent non-overlapping comparisons (7.5 comparisons) with only 2 cutting surfaces, we would effectively have 15 independent comparisons. Using this information, we can calculate the probability of at least one false positive to be `r sprintf("%0.04f%%", 1-(1-fpr)^comparisons * 100)` as shown in Equation \ref{eq:fpr}. While far more comparisons are likely to be performed, these comparisons may have some dependencies (at which point our formula would need to account for the covariance between successive comparisons). Ultimately, the number of comparisons cannot drop below `r comparisons` without leaving some evidence unexamined, which means this overall false positive rate is the lower bound.
